\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-15 main.Rmd
added two more paragraphs to case study

```{r flinders-2016, fig.height = 6.5, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a $3 \\times 4$ monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent."}
```

@@

```{r flinders-polar, fig.height = 6.5, fig.cap = "Figure \\ref{fig:flinders-2016} in circular layout, which is referred to as star plots. The daily periodicity on work days are clearly visible."}
```

@@

```{r flinders-free, fig.height = 6.5, fig.cap = "Line glyphs on the calendar format showing hourly foot traffic at Flinders Street Station, scaled over all the days. The individual shape on a single day becomes more distinctive, however it is impossible to compare the size of peaks between days."}
```

@@

```{r dow, fig.height = 7, fig.cap = "Letter value plot of daily energy usage against day of week by households. The enery consumed by household 2 exhibits much larger variability, cotrast to the rest households. Households 1, 2, and 4 use mose energy over the weekends."}
```

```{r hod, fig.height = 6, fig.cap = ""}
```

```{r household23, fig.height = 11, fig.cap = ""}
```

>>>>

```{r flinders-2016, fig.height = 7, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a $3 \\times 4$ monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent."}
```

@@

```{r flinders-polar, fig.height = 7, fig.cap = "Figure \\ref{fig:flinders-2016} in circular layout, which is referred to as star plots. The daily periodicity on work days are clearly visible."}
```

@@

```{r flinders-free, fig.height = 7, fig.cap = "Line glyphs on the calendar format showing hourly foot traffic at Flinders Street Station, scaled over all the days. The individual shape on a single day becomes more distinctive, however it is impossible to compare the size of peaks between days."}
```

@@

```{r dow, fig.height = 7, fig.cap = "Letter value plot of daily energy usage against day of week by households. The enery consumed by household 2 exhibits much larger variability, compared to the rest households. Households 1, 2, and 4 use mose energy over the weekends."}
```

Then a snapshot is taken at a different time resolution to picture individual's energy usage against time of day, across workdays and non-work days. Figure \ref{fig:hod} gives a more detailed depiction of each household's life style. Household 1 appears an early bird, starting the day before 6 and going back home around 18 on workdays. There is an uncommon pattern occurring to household 2 only, with a cluster of points concentrated above 1 kWh across all time of day. It perhaps alerts household 2 to potential electricity leakage. Household 3 shows persistent trimodel behaviors across workdays and non-workdays. Nevertheless, the non-work life of household 4 distinguishes from the workdays when most energy is consumed after 18.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between time of day and half-hourly energy usage, constrasting workdays and non-work days for each household. A distinctive pattern exclusive to household 2 is popped out: a fair amount of points are clustered above 1 kWh over all time of day."}
```

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households. Is there any untold story from these plots? Figure \ref{fig:household13} lays out the data points at the finest time resolution in a $3 \times 4$ monthly grid, for household 1 and 3. Household 1 was on vacation over three weeks of June, and household 2 was also away for holidays from September to early October and late June to mid July in the past year. This calendar plot evidently fills the missing piece of the picture.

```{r household13, fig.height = 11, fig.cap = "Arranging sub-daily energy usage into monthly grids reveals the vacation time periods for households 1 and 3, which are hidden in Figure \\ref{fig:dow} and \\ref{fig:hod}."}
```

### 2018-10-15 main.tex
added two more paragraphs to case study

\caption{Letter value plot of daily energy usage against day of week by households. The enery consumed by household 2 exhibits much larger variability, cotrast to the rest households. Households 1, 2, and 4 use mose energy over the weekends.}\label{fig:dow}
\end{figure}

@@

\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{figure/household23-1}

@@

\end{figure}

>>>>

\caption{Letter value plot of daily energy usage against day of week by households. The enery consumed by household 2 exhibits much larger variability, compared to the rest households. Households 1, 2, and 4 use mose energy over the weekends.}\label{fig:dow}
\end{figure}

Then a snapshot is taken at a different time resolution to picture
individual's energy usage against time of day, across workdays and
non-work days. Figure \ref{fig:hod} gives a more detailed depiction of
each household's life style. Household 1 appears an early bird, starting
the day before 6 and going back home around 18 on workdays. There is an
uncommon pattern occurring to household 2 only, with a cluster of points
concentrated above 1 kWh across all time of day. It perhaps alerts
household 2 to potential electricity leakage. Household 3 shows
persistent trimodel behaviors across workdays and non-workdays.
Nevertheless, the non-work life of household 4 distinguishes from the
workdays when most energy is consumed after 18.

@@

\caption{Scatterplot between time of day and half-hourly energy usage, constrasting workdays and non-work days for each household. A distinctive pattern exclusive to household 2 is popped out: a fair amount of points are clustered above 1 kWh over all time of day.}\label{fig:hod}
\end{figure}

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical
toolkits, are useful for summarizing overall deviations across days and
households. Is there any untold story from these plots? Figure
\ref{fig:household13} lays out the data points at the finest time
resolution in a \(3 \times 4\) monthly grid, for household 1 and 3.
Household 1 was on vacation over three weeks of June, and household 2
was also away for holidays from September to early October and late June
to mid July in the past year. This calendar plot evidently fills the
missing piece of the picture.

@@

{\centering \includegraphics[width=\textwidth]{figure/household13-1}

@@

\caption{Arranging sub-daily energy usage into monthly grids reveals the vacation time periods for households 1 and 3, which are hidden in Figure \ref{fig:dow} and \ref{fig:hod}.}\label{fig:household13}
\end{figure}
